Gringo 2.0\\--Draft--

### 2008-09-04 doc/documentation/paper.tex
Doku: added explanation of new errors and warnings
git-svn-id: https://potassco.svn.sourceforge.net/svnroot/potassco/branches/gringo2@492 3e02f596-3131-0410-8352-e04eeaec37cc

\subsection{Errors}
gringo2.0 stops the execution and prints an error message to standard error output.
\begin{itemize}
 \item 
\begin{verbatim}
 "the following rule cannot not be grounded,
  non domain predicates : { ... }"
\end{verbatim}
This error message gives a list of predicates that are not domain restricted.
You explicitly have to give a domain for those predicates.
 \item 
\begin{verbatim}
 "the following rule cannot not be grounded,
  weakly restricted variables: { ... }"
\end{verbatim}
This error message gives a list of variables that are not lambda restricted. 
\item
\begin{verbatim}
 "syntax error on line Y column Z unexpected token: X"
\end{verbatim}
The parser can not read the input format. Some unexpected token occurred in the input file.
\item
\begin{verbatim}
 "sorry clasp cannot handle disjunctive rules!"
\end{verbatim}
If using clingo or iclingo, this happens if disjunctive rules are used. Please choose another solver that support disjunctive rules.
\item
\begin{verbatim}
 "A fixed number of incremental steps is needed to ground the program."
\end{verbatim}
TODO: I dont know.
\item
\begin{verbatim}
 "cyclic constant definition."
\end{verbatim}
TODO: I dont know.
\item
\begin{verbatim}
 "The following statement cant be used with the incremental interface: X."
 "unsupported statement."
\end{verbatim}
TODO: I dont know.
\item
\begin{verbatim}
 "output does not support getIncUid."
\end{verbatim}
TODO: I dont know.
\item
\begin{verbatim}
 "comparing different types"
\end{verbatim}
TODO: I dont know.
\item
\begin{verbatim}
 "comparing function symbols"
\end{verbatim}
TODO: I dont know.

>>>>

\subsection{Errors}
gringo2.0 stops the execution and prints an error message to standard error output.
\begin{itemize}
 \item 
\begin{verbatim}
 "the following rule cannot not be grounded,
  non domain predicates : { ... }"
\end{verbatim}
This error message gives a list of predicates that are not domain restricted.
You explicitly have to give a domain for those predicates.
 \item 
\begin{verbatim}
 "the following rule cannot not be grounded,
  weakly restricted variables: { ... }"
\end{verbatim}
This error message gives a list of variables that are not lambda restricted. 
\item
\begin{verbatim}
 "syntax error on line Y column Z unexpected token: X"
\end{verbatim}
The parser can not read the input format. Some unexpected token occurred in the input file.
\item
\begin{verbatim}
 "sorry clasp cannot handle disjunctive rules!"
\end{verbatim}
If using clingo or iclingo, this happens if disjunctive rules are used. Please choose another solver that support disjunctive rules.
\item
\begin{verbatim}
 "A fixed number of incremental steps is needed to ground the program."
\end{verbatim}
This error occurs if an incremental program is given to gringo without using the option \texttt{--ifixed} or iclingo.
\item
\begin{verbatim}
 "cyclic constant definition."
\end{verbatim}
A cyclic definition of a constant is not allowed as shown in the example.
\begin{verbatim}
 #const x=y.
 #const y=x.
\end{verbatim}
\item
\begin{verbatim}
 "The following statement cant be used with the incremental interface: X."
 "unsupported statement."
\end{verbatim}
It is not allowed to use an optimize (\texttt{minimize} or \texttt{maximize}) or \texttt{compute} statement in an incremental program.
\item
\begin{verbatim}
 "comparing different types"
 "comparing function symbols"
\end{verbatim}
This error occurs if trying to compare non compareable values or function symbols as in
\begin{verbatim}
 p :- 1 < s.
 p :- f(x) < f(y).
\end{verbatim}
